UMD Building Classification

### 2024-12-09 report/paper/draft.tex
minor edits

We trained a variety of different models with different hyperparameters and selected 5 for further testing. Parameters can be found on the github in \verb*|dataset/parms.ipynb|. All images were standardized at 224x224, using the SyRA synthesized rain test image set with a random augmentation pipeline.

@@

@@

However, both models suffered from a lack of diversity in the dataset, which led to overfitting on nonexistent features and a lack of improvement. This was exacerbated by the limited weather conditions and time of day we took photos, which resulted in a lack of diversity and strong overfitting on nonexistent features. Additionally, weather augmentation was not as diverse as might be necessary to prove robustness to real world conditions.

>>>>

We trained a variety of different models with different hyperparameters (batch size, momentum, warm up epochs, pseudo label threshold, etc) and selected 5 for further testing. Parameters can be found on the github in \verb*|dataset/parms.ipynb|. All images were standardized at 224x224, using the SyRA synthesized rain test image set with a random augmentation pipeline.

@@

After each epoch, the human was asked to confirm or deny the accuracy of the model's prediction, and asked a region of the image for the model to focus on more based on the Grad-CAM feedback.

@@

However, both models suffered from a lack of diversity in the dataset, which led to overfitting on nonexistent features and a lack of improvement. Advancement on FixMatch can be achieved via cleaning up the dataset (eg less noise). Additionally, multiple classes can be defined for various parts of buildings (i.e. Atlantic Building looks very different depending on the angle)
